--- 
title: "Rare but useful R functions"
author: "Lingyun Zhang"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
link-citations: yes
links-as-notes: true
colorlinks: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Preface {-}

This is a book written for myself. Having said that, the meanings of "rare" and "useful" in the book title are totally decided/interpreted by one person, i.e. me--that is great freedom to me!

Actually, I pick up the functions in a random manner. Often, when I read other people's R code, if I see
a function which is "rare and useful", then I will include it in this book. Good fun, isn't it?

This book contains five (tentative) sections: 1. For creating data; 2. For processing data; 3. For logical checking; 4. For plotting; and 5. For other purposes.



# For creating data {-}

## `base::outer()` 

**Description**:`outer(x, y, FUN)` is to create a matrix with $m$ rows and $n$ columns, where $m$ and $n$ are lengths of `x` and `y`, respectively. The entry at $i, \ j$ position is given by `FUN(x[i], y[j])`. 

**Example 1**: Create a times table.
```{r}
(outer(1:9, 1:9, FUN = "*"))
```

**Example 2**: Create x-y coordinates.

```{r}
x <- Re(as.vector(outer(1:3, 1i*(1:3), FUN = "+")))
y <- Im(as.vector(outer(1:3, 1i*(1:3), FUN = "+")))
```


# For processing data {-}

# For logical checking {-}

## `rlang::is_empty()`

**Example**:
```{r, warning=FALSE, message=FALSE}
library(rlang)

(is_empty(NULL))
(is_empty(list()))
(is_empty(list(NULL)))
(is_empty(NA))
(is_empty(character(0)))
(is_empty(numeric(0)))
(is_empty(logical()))
(is_empty(NaN))
```





# For plotting {-}

# For other purposes {-}
